%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {MillenniumIT (Pvt) Ltd. Part of London stock exchange group} % Organization
    {Malabe, Sri Lanka} % Location
    {Jun. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {I am currently working on Post Trade product of Singapore Stock Exchange (SGX). I have contributed to development of several gateways such as 		\textbf{Downstream gateway, SBL Interface, SGXNetGateway} and engines such as \textbf{IPO engine}. Currently I am developing a testing framework 		called FortressPT which allows to write tests using domain specific objects for Post Trade software solution.}
		\subitem {\textbf{Downstream Gateway} – This is the gateway that delivers the transaction messages to downstream system for interfacing. }
		\subitem {\textbf{SBL Interface} – Securities Borrowing and Lending Interface. This interface acts as an interface between two depositories for securities borrowing and lending activities.}
		\subitem {\textbf{SGXNet Gateway} – This is an interface for receiving corporate action announcements for the Post trade system.}
		\subitem {\textbf{FortressPT} – This is a testing framework that allows user to test the Post Trade system using Domain specific objects.}
	\item {Built automated bamboo CI pipeline to automate regression testing}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Proavos (Private) Ltd.} % Organization
    {Colombo, Sri Lanka} % Location
    {Nov. 2015 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {During the internship period I developed a framework for Airline \textbf{BSP (Billing and Settlement Plan)} system}
	\item {During the internship I developed skills on how to build a framework/Project from scratch. Starting from designing class diagrams, modeling the system and using different design patterns to make the framework better}
	\item {During the period of internship I gained experience in JavaEE, Javascript, WildFly, JSP, Linux, FreeMarker and Domain knowledge on Avaition Industry Business aspects}
        \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
