%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Fortress - PT} % Organization/group/project
    {MillenniumIT - project} % Location
    {Feb. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {This is a testing framework that is used to test Millennium Post Trade system. With the help of this framework users can write tests suites using 		domain specific objects without worrying about underlying system specific technical details.}
        \item {\textbf{Technologies and Standards}: Java 8, MQ, MVEL, FIXML, SWIFT, SESE}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Private Cloud Management Platform – CloudBox } % Organization/group/project
    {Final year project} % Location
    {Apr. 2016 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {CloudBox is a personal cloud product targeted for small companies and homes. This product will enable the user to create a local private cloud within his home or company with minimal technical expertise. The objectives of this project are to minimize the data usage of the cloud platform by reducing unwanted synchronizations, develop a management console that can simplify the usage and management of the cloud platform for the end user and develop a reliable and efficient private cloud platform for a small company or home. A web based System which manages Human resource, inventory and orders of an Audio Supplying Company.}
        \item {\textbf{Mentor: }:  Prof. Gihan Dias}
	\item {\textbf{Paper: }:   Three-tier Private Cloud Application Management System with On-Site Hardware (Published in International Symposium On 
Parallel and Distributed Computing (ISPDC), 2017 16th International Symposium)}
	\item {\textbf{Link:  }:  \url{http://ieeexplore.ieee.org/document/8121619/}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Designer/Developer} % Affiliation/role
    {Billing and Settlement Plan framework} % Organization/group/project
    {Internship Project} % Location
    {Nov. 2015 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {In my internship I developed a framework that enables airlines to publish agent sales data to the BSP (Billing and settlement Plan) system.}
        \item {This framework is used to retrieve and encode the sales data into IATA standard and publish it to a BSP system server automatically.}
        \item {\textbf{Technologies: } Java EE, SFTP, HTML, CSS, JavaScript}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Designer/Developer} % Affiliation/role
    {Big Data Project – Tool for visualize different aspects of a social network} % Organization/group/project
    {} % Location
    {Jan. 2015 - May. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {This is a tool for visualize and analyze a social network. When the user inputs a shapefile and data of a social network through a CSV file this tool visualizes the network and allow user to see different statistical measures of the network. }
        \item {This framework is used to retrieve and encode the sales data into IATA standard and publish it to a BSP system server automatically.}
        \item {\textbf{Technologies: } JavaScript, D3.js }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Sales Leads Management System  } % Organization/group/project
    {} % Location
    {May. 2014 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {This is a standalone ERP system developed for government sales division of Sri Lanka Telecom PLC. This is a standalone ERP system to track record and analyze sales Leads until a fully comprehensive ERP system is implemented.}
        \item {This application can record, monitor, analyze sales Leads and generate performance reports for a time period.}
        \item {Apart from that it supported to analyze the performance of sales managers and indicate them to their superiors.}
        \item {\textbf{Technologies: } C\#, MySQL }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Image based ballot-paper (vote) counting software } % Organization/group/project
    {} % Location
    {Apr. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {This software was developed to read, count and classify Sri Lankan parliamentary election ballot papers. This software can recognize the party and up to three preferential votes. Software would process all the ballot papers assigned to it and output the cumulative results to the users.}
        \item {This application can record, monitor, analyze sales Leads and generate performance reports for a time period.}
        \item {Apart from that it supported to analyze the performance of sales managers and indicate them to their superiors.}
        \item {\textbf{Technologies: } OpenCV, C++}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
