%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Organizing Committee President} % Affiliation/role
    {YEP 4.0 (Youth Empowerment Project)} % Organization/group
    {AIESEC COLOMBO SOUTH} % Location
    {Mar. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Youth Empowerment Project is a community development project aimed to improve leadership and entrepreneurial skills of Sri Lankan youth}
        \item {This project was carried out for 6 weeks in Sri Lanka. Volunteers from various parts of the world joined this program through AIESEC and helped to deliver better program for Sri Lankan youth.}
        \item {As the Organizing Committee president I organized and carried out the program.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Organizing Committee Vice president} % Affiliation/role
    {Corp Hunt 3} % Organization/group
    {AIESEC Colombo South} % Location
    {Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {This program was initaited to provide Global Internship programs in Sri Lanks to university students around the world.}
        \item {As Organizing committee vice president I pitched this ideas to companies in Sri Lanka to provide internship programs to University Students.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {IFly - Out Going Exchange program} % Organization/group
    {AIESEC COLOMBO SOUTH} % Location
    {2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {This program was initiated to provide global internships to university students in Sri Lanka}
        \item {As a member of this program I matched students in Sri Lanka to various internship programs all over the world and trained them to work in various such environments. }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
